\section{Evaluation}
\label{sec:evaluation}

In this section, we first present some comparisons on accuracy. Then, to show the performance improvement of local feature descriptor by using {\sys}, an evaluation is also performed on {\sys} combined with SIFT and SURF, two most widely used {\lfea}s.

\subsection{Experimental Comparison}
\label{sec:evaluation_comparison}

\begin{table}[!t]
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
 & P & R & F1 & RE & SM(ms) & SG(ms) \\
\hline\hline
GBSR   & 0.81 & 0.86 & 0.83 & 39\% & 178 & 2086 \\
{\sys} & 0.52 & 0.59 & 0.55 & 42\% & N/A & 3.2 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison between GBSR and {\sys} in precision (P), recall (R), F1 score, reduction efficiency (RE), saliency map (SM) and segmentation (SG) processing time in milliseconds.}
\label{tab:comparison}
\end{table}

As mentioned in Section~\ref{sec:introduction}, we target to design an algorithm for local feature reduction using salient region. To achieve good performance, an approximate salient region detection is involved. Although our approach cannot detect precise salient region, we are still interested in evaluating its precision against general purpose ones. Here we compare {\sys} with a previous research called GBSR (Global Contrast based Salient Region) by Cheng et al.~\cite{cheng2011global}. GBSR is a state-of-the-art salient region detection algorithm written in C++, which makes us easy to compare the computation efficiency with ours. To be used in feature elimination, we also perform GBSR's own segmentation approach to get the salient region boundary. It means in our evaluation the processing time of GBSR includes not only the saliency map detection but also the segmentation.

Since we only focus on local features, our evaluation differs from regular salient region researches: the precision and recall are given according to the results of local feature reduction, not the precise salient region boundary. The evaluated dataset is provided by Achanta et at.~\cite{achanta2009frequency}, which is a subset of the public image database from Liu et at.~\cite{liu2011learning}. As input, we first generate local features for the whole database with OpenSURF~\cite{evans2010opensurf}. 

As shown in the column 2, 3 and 4 of Table~\ref{tab:comparison}, {\sys} gets lower precision lower recall compared to GBSR. The reduction efficiency in the column 5 refers to the proportion of the left local features after a reduction. The results shows that both of them can help to eliminate more than half of the original features. As discussed in Section~\ref{sec:algorithm}, some limitations in our salient region detection approach prevents processing images with high texture background or overlapping objects correctly. With a obvious precision gap compared to the state-of-the-art approach, the salient region used in {\sys} is not suitable for general purpose scenarios.

To compare the efficiency of these two algorithms, we run {\sys} and GBSR both on a PC with one Intel Quad Core 2.4Ghz CPU and 4GB memory. The result in the column 6 of Table~\ref{tab:comparison} shows that the well optimized GBSR costs average 2086 milliseconds to get the final salient region for one image, while {\sys} only costs 3.2 milliseconds. Even only counting the time for saliency map detection, GBSR still needs average 178 milliseconds. The performance result of {\sys} is very impressive but not surprising, because the computation of {\sys} is really simple and straightforward.

\subsection{Local Feature Descriptor Integration}
\label{sec:evaluation_integration}

{\sys} is designed to improve the performance of local feature descriptor. To evaluate whether {\sys} satisfies this design purpose, we integrate our algorithm into the OpenSIFT~\footnote{http://robwhess.github.com/opensift/} and OpenSURF~\footnote{http://www.chrisevansdev.com/computer-vision-opensurf.html} to see the actual effects. The salient region detection is carefully added between the detection stage and the description stage. It means {\sys} can reuse the computation results directly from the detection stage. After the reduction of {\sys}, the computation of the description stage should be much smaller, since it's only related to the amount of local features.

Furthermore, we also implement a whole image retrieval system for evaluation. The system first builds a VOC-Tree~\cite{nister-stewenius-cvpr-2006} by using SIFT or SURF feature vectors extracted from image datasets. Then, each incoming query image is transfered into feature vectors too and compared in that VOC-Tree. At last, the found top similar images would be reordered by using RANSAC~\cite{ransac1981}. To involve {\sys}, we just replace the original local feature descriptor with a {\sys} enabled version.

The input for evaluation is an image retrial dataset by Nist\'er et al.~\cite{nister-stewenius-cvpr-2006} with 10200 VGA ($640\times480$ pixels) photos. And the whole experiment is performed on a server with a Intel Quad Core i7 3.4Ghz CPU and 4GB RAM. Table~\ref{tab:integration} shows the final performance results. Compared to the original local feature algorithm, {\sys} helps to improve the local feature descriptor performance by about 1.6X. And by reducing local features, the whole image retrieval system gains a more than 2X speedup in both building and query phase.

We also present the accuracy influence of introducing {\sys} to our retrieval system in the column 5 of Table~\ref{tab:integration}. Here, the retrieval results of different algorithms are scored following the method of Nist\'er et al.~\cite{nister-stewenius-cvpr-2006}. Then we get the accuracy by dividing the score of {\sys} enabled algorithms by of original ones. {\sys} based algorithms show a small accuracy loss of about 7 percent. Considering the great speedup provided by {\sys}, we regard this result as acceptable.

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
 & DES & BLD & QRY & ACY \\
\hline\hline
SIFT & 0.54s & 0.33s & 1.65s & - \\
SIFT-{\sys} & 0.33s & 0.12s & 0.77s & 93\% \\
\hline\hline
SURF & 0.15s & 0.06s & 0.54s & - \\
SURF-{\sys} & 0.09s & 0.03s & 0.34s & 94\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparison between original {\lfea}s and {\sys} enabled ones. DES refers to {\lfea} time. BLD refers to VOC-Tree building time. QRY includes VOC-Tree query time and RANSAC time. ACY refers to the accuracy of the {\sys} enabled retrieval system compared to the original ones.}
\label{tab:integration}
\end{table}